\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/background.tex
something
grammar

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was designed based on \ac{USB}. \ac{HID} is
designed with to unify the implementation for devices like mice,
keyboards, etc. Before its appearance, the standard is divided between
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own driver to work. After \ac{HID}, users only need to
write one driver for an entire class of \acp{HID}. Furthermore, the \ac{HID} standard also
requires all devices to be \ac{PnP}, which is indeed
convenient but insecure too.

In 1998, the first widely supported \ac{USB} protocol was designed. \ac{USB} 1.1~\cite{usb11}
provided two data transfer rates which are low speed (1.5 Mbit/s) and full
speed (12 MBit/s). At this point, due to the transfer limit, it only supports
limited types of devices like keyboards, mice, etc.

>>>>

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was designed based on \ac{USB}. \ac{HID} is
designed to unify the implementation for devices like mice,
keyboards, etc. Before its appearance, the standard is divided among
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own driver to work. After \ac{HID}, users only need to
write one driver for an entire class of \acp{HID}. Furthermore, the \ac{HID} standard also
requires all devices to be \ac{PnP}, which is indeed
convenient but insecure too.

In 1998, the first widely supported \ac{USB} protocol was designed. \ac{USB} 1.1~\cite{usb11}
provided two data transfer rates which are low speed (1.5 Mbit/s) and full
speed (12 MBit/s). At this point, due to the transfer limitation, it only supports
limited types of devices like keyboards, mice, etc.

### 2021-03-22 WOOT/Files/badusb.tex
grammar

As introduced in Section~\ref{sec:related_work},
existing works~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal \ac{HID} devices and utilize the \ac{USB} protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as \acp{HID} (e.g. keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to lack of \ac{UI} status. Whatever \acp{HID} the
attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
check the status information, which makes it nearly impossible to carry out
their attacks precisely or know the effects after attacks.

@@

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse movements. Thus, the
attacker can execute arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's device. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

The advantage of this mode is that it achieves attack
feedback with video streaming.
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Also, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

@@

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirects it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movements from the attacker
through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.

>>>>

As introduced in Section~\ref{sec:related_work},
existing works~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal \ac{HID} devices and utilize the \ac{USB} protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as \acp{HID} (e.g. keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to a lack of \ac{UI} status. Whatever \acp{HID} the
attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
check the status information, which makes it nearly impossible to carry out
their attacks precisely or know the effects after attacks.

@@

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packets to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse movements. Thus, attackers can execute arbitrary scripts on the victim's device. This is the
function of BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movements injection, an attacker can obtain real-time feedback from the victim's device. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

The advantage of this mode is that it achieves attack
feedback with video streaming.
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Also, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks.

@@

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirects it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movements from the attacker
through GSM/WiFi and replays them to the victim's device by the \ac{USB} emulation.

### 2021-03-22 WOOT/Files/countermeasure.tex
grammar

\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy. For example, 
in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
functionality only after being authorized by the user. 
Defense like USB Condom distrusts all types of \ac{USB} devices by blocking data channels and stopping all \ac{USB} functions other than charging.
Such defense methods effectively stop attacks 
like \tool.

\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
is actually unable to mirror the lock screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the lock screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated \ac{UI} Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
is secure the other is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the ``password'' and ``keyboard'' are recognized as sensitive while other parts of content are insensitive. Thus, the ``password'' and ``keyboard'' are not rendered on untrusted screen.

>>>>

\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} devices -- applying the \textit{distrust-by-default} policy. For example, 
in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
functionality only after being authorized by the user. 
Defense like USB Condom distrusts all types of \ac{USB} devices by blocking data channels and stopping all \ac{USB} functions other than charging.
Such defense methods effectively stop attacks 
like \tool.

\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
is actually unable to mirror the lock screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the lock screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated \ac{UI} Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
is secure the another is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
could only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the ``password'' and ``keyboard'' are recognized as sensitive while other parts of content are insensitive. Thus, the ``password'' and ``keyboard'' are not rendered on untrusted screen.

### 2021-03-22 WOOT/Files/discussion.tex
Unsubstantiated sentence
grammar

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
Depending on the victim's settings, the \tool may be used as an extended monitor or be set to `Desktop Mode' or not be enabled at all. Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen. But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring.
Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
 Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol. There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}. Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones. But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

@@

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  
Since non-professional users often neglect checking the security of plug-in \ac{USB} devices, they are often unaware of the attacks from \tool.
can be hardly detected by them while attacks are performing.  
The popularity and universality of public \ac{USB} devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface and controlling the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
Depending on the victim's settings, the \tool may be used as an extended monitor or be set to `Desktop Mode' or not be enabled at all. Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen. But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring the screen.
Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
 Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol. There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}. Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones. But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

@@

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities~\cite{li2018usb}, which makes \tool more influential.  
Since non-professional users may neglect checking the security of plug-in \ac{USB} devices, 
they may unaware of the attacks from \tool.
can be hardly detected by them while attacks are performing.  
The popularity and universality of public \ac{USB} devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface and controlling the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

### 2021-03-22 WOOT/Files/experiment.tex
grammar

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device to mirror the primary screen. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen. In EMUI, there is a special mode called ``Desktop Mode'', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is enabled, as victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
device in this experiment.  Besides disguising as normal \acp{HID} like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After establishing the connection, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via the victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

Next, we summarize the possible threats toward users under different modes.
%\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

>>>>

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device to mirror the primary screen. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and it is similar in Windows 10. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen. In EMUI, there is a special mode called ``Desktop Mode'', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is enabled, as victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target devices. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of them resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
device in this experiment.  Besides disguising themself as normal \acp{HID} like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After establishing the connection, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via the victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

Next, we summarize the possible threats toward users under different modes.
%\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data could be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' devices and could conduct any actions on the victims' devices.

### 2021-03-22 WOOT/Files/introduction.tex
grammar

The \ac{USB} protocol has become popular worldwide
since its appearance in 1996, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

@@

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

The \ac{USB} protocol has become popular worldwide
since its appearance in 1996, as it provides a unified and easy-to-use approach for an
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

@@

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
